---
title: "p8105_hw1_ww2745"
output: github_document
date: "2024-09-21"
---

Here are solutions for HW1.

```{r setup, include = FALSE}
library(palmerpenguins)
library(ggplot2)
library(tidyverse)
```

# Problem 1

First, we load the penguins data set and do a descriptive analysis.

```{r load_dataset}
data("penguins", package = "palmerpenguins")
mean_fl=mean(penguins$flipper_length_mm, na.rm = TRUE)
```

This is a dataset about penguins. It includes information for following features: `r paste(colnames(penguins), collapse = ', ')`.
For the size of the dataset, it has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
The mean of the flipper length is `r round(mean_fl, digits = 2)` mm.

Then, we make a scatterplot of `flipper_length_mm `(y) vs `bill_length_mm`(x).

```{r yx_scatter}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave(filename = "scatterplot_p1.png")
```

# Problem 2
Create a data frame comprised of:

a random sample of size 10 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”

```{r create_df}
set.seed(123)
p2_df <- tibble(
  random_sample = rnorm(10),                        
  greater_than_zero = random_sample > 0,          
  character_vector = sample(letters[1:6], 10, replace = TRUE),  
  factor_vector = factor(sample(c("Level 1", "Level 2", "Level 3"), 10, replace = TRUE))  
)

```

